The Input/Ouput Automata Library

### 2011-07-05 papers/paper1/paper.tex
Cleared send set upon failure.

\usepackage{acronym}

@@

>>>>

\usepackage{outline}

@@

\begin{outline}
\item We desire to build complex distributed systems
\item These systems are characterized by asynchrony and concurrency at both the macroscopic and microscopic levels.
  \begin{outline}
  \item Macroscopic - Operate in a network where computation is naturally concurrent and asynchronous.
  \item Microscopic - Individual devices perform more than one task and the physical world is asynchronous.
  \end{outline}
\item In spite of the importance of asynchrony and concurrency, we build these systems using the thread abstraction which is awkward and difficult.

\end{outline}
